### 2015-07-27 abstract.tex
Adding appendix

In this work, we cast the well-known Poisson surface reconstruction algorithm into a more general setting, we reformulate it in terms of shift invariant spaces (spaces that are spanned by lattice translates of an admissible generating function). The treatment is general, but our specific interest is in reconstructing a surface of a solid model from an oriented point-set within function spaces defined over the body centred cubic lattice. We also propose a general framework for approximating the solution to Poisson's equation in a hypercube with zero Dirichlet boundary conditions, and a new variational scheme to re-sample the initial oriented point-set onto a regular grid. Once the points have been re-sampled onto a grid, the rest of the pipeline is purely based on digital filtering. We also analyze the error incurred via the digital filtering approximation methodology and propose a Fourier domain error kernel that can be used to design solution filters that fully exploit the approximation capabilities of the target space. Finally, we show that a host of Poisson-like methods fail to take advantage of the full approximation spaces over which they are defined.

>>>>

In this work, we cast the well-known Poisson surface reconstruction algorithm into a more general setting -- we reformulate it in terms of shift invariant spaces (spaces that are spanned by lattice translates of an admissible generating function). The treatment is general, but our specific interest is in reconstructing a surface of a solid model from an oriented point-set within function spaces defined over the body centred cubic lattice. We also propose a general framework for approximating the solution to Poisson's equation in a hypercube with zero Dirichlet boundary conditions, and a new variational scheme to re-sample the initial oriented point-set onto a regular grid. Once the points have been re-sampled onto a grid, the rest of the pipeline is purely based on digital filtering. We also analyze the error incurred via the digital filtering approximation methodology and propose a Fourier domain error kernel that can be used to design solution filters that fully exploit the approximation capabilities of the target space. Finally, we show that a host of Poisson-like methods fail to take advantage of the full approximation spaces over which they are defined.

### 2015-07-27 poisson_errker.tex
Adding appendix

\subsection{Approximate Solution} \sec{sub:approximatesol}
We are interested in the scenario where the function $f$ is only known
through its point samples. Specifically, we assume that the samples of
$f$ reside on the sites of the lattice $\lattice{L}_h$. For the
purpose of enumerating the samples that are contained within
$\cube^s$, let us define the point set
\begin{equation}
  \pointset{T}_h := \underbrace{\{\vect{x}_1,\ldots,\vect{x}_{2^sN} \}}_{\pointset{I}_h}
  \cup
\underbrace{\{\vect{x}_{2^sN + 1},\ldots,\vect{x}_{2^sN + M} \}}_{\pointset{B}_h},
\end{equation}
where $\pointset{I}_h := \ocube^s \cap \{\vect{x} + \vect{m} :
\vect{x} \in \lattice{L}_h \cap \oucube^s, \vect{m} \in \ints^s \}$
consists of interior lattice points, while $\pointset{B}_h$ consists
of extended boundary points, i.e. $\pointset{B}_h := (\lattice{L}_h
\cap \partial\cube^s \cap (-1,1]^s) \cup (\lattice{L}_h \cap
\ocube^s\backslash \pointset{I}_h)$. Two dimensional illustrations are
shown in Figure~\ref{fig:pointset}. We note that with the above
definition of $\pointset{I}_h$, the points $\vect{x}_j$ for $j \in
\{1, \ldots, N\}$ are contained in the open unit cube $\oucube^s$
whereas the remaining points ($\vect{x}_j$ for $j \in \{N+1, \ldots,
2^sN\}$) lie outside. Furthermore, we assume
that the lattice $\lattice{L}$ and the sampling rate $h$ are such that
the set $\{\vect{x} + 2\vect{m} : \vect{x} \in \pointset{T}_h,
\vect{m} \in \ints^s\} = \lattice{L}_h$. We remark that this
requirement for $\lattice{L}_h$ is also
satisfied by integration lattices that are commonly used
to devise quadrature rules within the unit cube $\ucube^s$~\cite{nied92}.
\begin{figure}[t]
  \centering
  \subfloat[Cartesian]{\label{fig:cartesian}\input{./figures/2DCartesian}}
  \hspace{2em}
  \subfloat[Quincunx]{\label{fig:quincunx}\input{./figures/2DQuincunx}}
  \caption[Interior and boundary samples]{Illustration of the point set
  $\pointset{T}_h$ on the two
    dimensional Cartesian ($\mat{L} = \bigl( \begin{smallmatrix} 1&0\\
      0&1
    \end{smallmatrix} \bigr)$, $h=\tfrac{1}{8}$) and Quincunx ($\mat{L} = \bigl(
    \begin{smallmatrix} 1&-1\\
      1&1
    \end{smallmatrix} \bigr)$, $h=\tfrac{1}{10}$) lattices. The interior points
    ($\bullet$) belong to the set $\pointset{I}_h$ while the extended
    boundary points ($\circ$) belong to $\pointset{B}_h$.}
  \label{fig:pointset}
\end{figure}

@@

\subsection{Relationship to the Galerkin method}
\label{sec:Galerkin}
The modified residue error kernel~\eqref{eq:opResidue} can also be analyzed in light of the Galerkin method~\cite{quarteroni08} using a weak formulation of the Poisson equation~\eqref{eq:PoissonEquation}, where the trial and test spaces are the same with the notable difference that the spaces are not required to explicitly satisfy any particular boundary conditions. Rather, a zero boundary condition is implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be odd as explained in~\SC{sub:approximatesol}. Here, we establish the connection for the homogeneous case but the analysis also easily extends to the non-homogeneous case, as well as to other types of differential operators.

@@

On the other hand, if the point samples of $f$ are already available (i.e. $\analysis{\varphi} = \delta$) and the orthogonal projection cannot be realized, then the goal of the asymptotically optimal
procedure is to find a suitable correction filter $\gamma$ such that $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ where $k = \order{\lattice{L}}{\varphi}$.  
%If we define the analysis function
%$\phi(\vect{x}) := \sum_{\vect{k} \in \ints^s} t[\vect{x}]
%\delta(\vect{k} - \mat{L}\vect{k})$, then the criterion
%$E_{\mathsf{res}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ is
%equivalent to the requirement that the moments of $\phi$ and
%$\invlaplacian \dual{\varphi}$ (here
%$\ftpairs{\invlaplacian}{(-4\pi^2\norm{\vect{\omega}}^2)^{-1}}$) match
%up to the order $k$, i.e.  $\int_{\reel^s}
%\vect{x}^{\vect{\mu}}(\phi(\vect{x}) - \invlaplacian
%\dual{\varphi}(\vect{x})) d\vect{x} = 0$ for $0 \le \abs{\vect{\mu}} <
%k$. 
In other words, our approximation procedure attempts to reproduce the Galerkin orthogonality condition given by~\eqref{eq:GalerkinOrthogonality}. This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
in~\SC{sec:interpQuasiInterp}.

>>>>

\subsection{Approximate Solution} \label{sub:approximatesol}
We are interested in the scenario where the function $f$ is only known through its point samples. Specifically, we assume that the samples of $f$ reside on the sites of the lattice $\lattice{L}_h$. For the purpose of enumerating the samples that are contained within $\cube^s$, let us define the point set
\begin{equation}
  \pointset{T}_h := \underbrace{\{\vect{x}_1,\ldots,\vect{x}_{2^sN} \}}_{\pointset{I}_h}
  \cup
\underbrace{\{\vect{x}_{2^sN + 1},\ldots,\vect{x}_{2^sN + M} \}}_{\pointset{B}_h},
\end{equation}
where $\pointset{I}_h := \ocube^s \cap \{\vect{x} + \vect{m} :
\vect{x} \in \lattice{L}_h \cap \oucube^s, \vect{m} \in \ints^s \}$
consists of interior lattice points, while $\pointset{B}_h$ consists
of extended boundary points, i.e. $\pointset{B}_h := (\lattice{L}_h
\cap \partial\cube^s \cap (-1,1]^s) \cup (\lattice{L}_h \cap
\ocube^s\backslash \pointset{I}_h)$. Two dimensional illustrations are
shown in Figure~\ref{fig:pointset}. We note that with the above
definition of $\pointset{I}_h$, the points $\vect{x}_j$ for $j \in
\{1, \ldots, N\}$ are contained in the open unit cube $\oucube^s$
whereas the remaining points ($\vect{x}_j$ for $j \in \{N+1, \ldots,
2^sN\}$) lie outside. Furthermore, we assume
that the lattice $\lattice{L}$ and the sampling rate $h$ are such that
the set $\{\vect{x} + 2\vect{m} : \vect{x} \in \pointset{T}_h,
\vect{m} \in \ints^s\} = \lattice{L}_h$. We remark that this
requirement for $\lattice{L}_h$ is also
satisfied by integration lattices that are commonly used
to devise quadrature rules within the unit cube $\ucube^s$~\cite{nied92}.
\begin{figure}[t]
  \centering
  \subfloat[Cartesian]{\label{fig:cartesian}\input{./figures/2DCartesian}}
  \hspace{2em}
  \subfloat[Quincunx]{\label{fig:quincunx}\input{./figures/2DQuincunx}}
  \caption[Interior and boundary samples]{Illustration of the point set
  $\pointset{T}_h$ on the two
    dimensional Cartesian ($\mat{L} = \bigl( \begin{smallmatrix} 1&0\\
      0&1
    \end{smallmatrix} \bigr)$, $h=\tfrac{1}{8}$) and Quincunx ($\mat{L} = \bigl(
    \begin{smallmatrix} 1&-1\\
      1&1
    \end{smallmatrix} \bigr)$, $h=\tfrac{1}{10}$) lattices. The interior points
    ($\bullet$) belong to the set $\pointset{I}_h$ while the extended
    boundary points ($\circ$) belong to $\pointset{B}_h$.}
  \label{fig:pointset}
\end{figure}

@@

\subsection{Relationship to the Galerkin method}
\label{sec:Galerkin}
The modified residue error kernel~\eqref{eq:opResidue} can also be analyzed in light of the Galerkin method~\cite{quarteroni08} using a weak formulation of the Poisson equation~\eqref{eq:PoissonEquation}, where the trial and test spaces are the same with the notable difference that the spaces are not required to explicitly satisfy any particular boundary conditions. Rather, a zero boundary condition is implicitly obtained by requiring that the solution coefficients $c[\cdot]$ be odd. % as explained in~\SC{sub:approximatesol}. 
Here, we establish the connection for the homogeneous case but the analysis also easily extends to the non-homogeneous case, as well as to other types of differential operators.

@@

On the other hand, if the point samples of $f$ are already available (i.e. $\analysis{\varphi} = \delta$) and the orthogonal projection cannot be realized, then the goal of the asymptotically optimal
procedure is to find a suitable correction filter $\gamma$ such that $E_{\mathsf{mod}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ where $k = \order{\lattice{L}}{\varphi}$.  
%If we define the analysis function
%$\phi(\vect{x}) := \sum_{\vect{k} \in \ints^s} t[\vect{x}]
%\delta(\vect{k} - \mat{L}\vect{k})$, then the criterion
%$E_{\mathsf{res}}(\vect{\omega}) = O(\norm{\vect{\omega}}^{2k})$ is
%equivalent to the requirement that the moments of $\phi$ and
%$\invlaplacian \dual{\varphi}$ (here
%$\ftpairs{\invlaplacian}{(-4\pi^2\norm{\vect{\omega}}^2)^{-1}}$) match
%up to the order $k$, i.e.  $\int_{\reel^s}
%\vect{x}^{\vect{\mu}}(\phi(\vect{x}) - \invlaplacian
%\dual{\varphi}(\vect{x})) d\vect{x} = 0$ for $0 \le \abs{\vect{\mu}} <
%k$. 
In other words, our approximation procedure attempts to reproduce the Galerkin orthogonality condition given by~\eqref{eq:GalerkinOrthogonality}. %This is akin to the quasi-interpolation condition~\eqref{eq:quasiCondition} introduced
in~\SC{sec:interpQuasiInterp}.
